### 2024-03-23 content/chapter_2.tex
:pencil: Add SWIPT modules and operation modes

	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
		Some preference of \gls{wit} and \gls{wpt} are inherently conflicting, for example:
		\begin{itemize}
			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
		\end{itemize}
		Those disparities translate to a fundamental tradeoff between information and power transfer in \gls{swipt} systems, which is often quantified by a convex \emph{\gls{r-e} region}.
		\begin{equation}
			\mathcal{C}_\mathrm{R-E}(P) \triangleq \Bigl\{ (r,e) : 0 \le r \le \log(1 + \gamma), \ 0 \le e \le z \Bigr\},
		\end{equation}
		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
	\end{subsection}

	\begin{subsection}{System Architecture}

		\begin{subsubsection}{Information and Energy Flows}

		\end{subsubsection}

		\begin{subsubsection}{Receiver Architectures}

		\end{subsubsection}
		As shown in Figs. \subref*{fg:swipt_colocated} and \subref*{fg:swipt_separated}, \gls{swipt} can be classified into two categories based on the receiver configuration:
		% \begin{itemize}
		% 	\item \emph{\gls{swipt}:} Energy and information are simultaneously delivered in the downlink to co-located and/or separated information receiver(s) and energy receiver(s);
		% 	\item \emph{\gls{wpcn}:} Energy is delivered in the downlink to active device(s) that generate and transmit information-bearing signals in the uplink;
		% 	\item \emph{\gls{wpbc}:} Energy is delivered in the downlink to passive node(s) that reflect part of incoming waves and embed information in the uplink.
		% \end{itemize}
		\begin{figure}[H]
			\centering
			\subfloat[\gls{swipt} with co-located receiver]{
				\resizebox{7cm}{!}{
					\input{assets/chapter_2/swipt_colocated.tex}
				}
				\label{fg:swipt_colocated}
			}
			\subfloat[\gls{swipt} with separated receivers]{
				\resizebox{7cm}{!}{
					\input{assets/chapter_2/swipt_separated.tex}
				}
				\label{fg:swipt_separated}
			}
			\\
			\subfloat[Monostatic backscatter]{
				\resizebox{7cm}{!}{
					\input{assets/chapter_2/backcom_monostatic.tex}
				}
				\label{fg:backcom_monostatic}
			}
			\subfloat[Bistatic backscatter]{
				\resizebox{7cm}{!}{
					\input{assets/chapter_2/backcom_bistatic.tex}
				}
				\label{fg:backcom_bistatic}
			}
			\caption{
				Information and energy flows in different WIPT schemes. Dashed and dotted lines denote energy and information flows, respectively.
			}
			\label{fg:wipt_schemes}
		\end{figure}

>>>>

	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
		Some preference of \gls{wit} and \gls{wpt} are inherently conflicting, for example:
		\begin{itemize}
			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
		\end{itemize}
		Those disparities translate to a fundamental tradeoff between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
		\begin{equation}
			\mathcal{C}_\mathrm{R-E}(P) \triangleq \Bigl\{ (r,e) : 0 \le r \le \log(1 + \gamma), \ 0 \le e \le z \Bigr\},
		\end{equation}
		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
	\end{subsection}

	\begin{subsection}{Modules and Operation Modes}
		\begin{subsubsection}{Information and Energy Flows}
			In \gls{swipt}, the information and energy are always transmitted from the same source while their receivers can be either co-located or separated, as shown in Figs. \subref*{fg:swipt_colocated} and \subref*{fg:swipt_separated}.
			This is different from \gls{bc} where the energy is delivered in the downlink and the information is sent in the uplink, as shown in Figs. \subref*{fg:backcom_monostatic} and \subref*{fg:backcom_bistatic}.
			\begin{figure}[H]
				\centering
				\subfloat[\gls{swipt} with co-located receiver]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/swipt_colocated.tex}
					}
					\label{fg:swipt_colocated}
				}
				\subfloat[\gls{swipt} with separated receivers]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/swipt_separated.tex}
					}
					\label{fg:swipt_separated}
				}
				\\
				\subfloat[Monostatic backscatter]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/backcom_monostatic.tex}
					}
					\label{fg:backcom_monostatic}
				}
				\subfloat[Bistatic backscatter]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/backcom_bistatic.tex}
					}
					\label{fg:backcom_bistatic}
				}
				\caption{
					Information and energy flows in \gls{swipt} and \gls{bc} systems. Blue and black parts denote information and power subsystems, respectively.
				}
				\label{fg:wipt_schemes}
			\end{figure}
			From a design perspective, co-located \gls{swipt} receiver is a more general model since it can exploit the received signal for either purpose or a mixture in between.
			We thus focus on this model in the following context.
		\end{subsubsection}

		\begin{subsubsection}{Receiver Architectures}
			Figure \ref{fg:swipt_receiver_architectures} illustrates four potential architectures for a co-located \gls{swipt} receiver \cite{Clerckx2022}:
			\begin{figure}[H]
				\centering
				\subfloat[Ideal receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ideal.tex}
					}
					\label{fg:receiver_ideal}
				}
				\\
				\subfloat[Time switching receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ts.tex}
					}
					\label{fg:receiver_ts}
				}
				\\
				\subfloat[Power splitting receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ps.tex}
					}
					\label{fg:receiver_ps}
				}
				\\
				\subfloat[Integrated receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_integrated.tex}
					}
					\label{fg:receiver_integrated}
				}
				\caption{
					Architectures of a co-located \gls{swipt} receiver.
				}
				\label{fg:swipt_receiver_architectures}
			\end{figure}

			\begin{itemize}
				\item \emph{Ideal receiver:} The received signal is used for both information decoding and energy harvesting. This is theoretically the most efficient design with a rectangle \gls{r-e} region but is unimplementable in practice due to hardware constraints.
				\item \emph{\gls{ts} receiver:} Each time frame is divided into individual \gls{wit} and \gls{wpt} phases, where the receiver switches between information decoder and energy harvester, respectively. The transmitted waveform and \gls{ris} response are optimized independently for each phase, and the resulting \gls{r-e} region is a triangle with two vertices corresponding to \gls{wit}-only and \gls{wpt}-only.
				\item \emph{\gls{ps} receiver:} The received signal is split into two parts with power ratio $\rho$ and $1{-}\rho$. The former is fed into the energy harvester and the latter is used for information decoding. The transmitter and \gls{ris} are jointly optimized for both purposes with the knowledge of splitting ratio, and the resulting \gls{r-e} region may be non-convex.
				\item \emph{Integrated receiver \cite{Kim2021a}:} The transmit signal is modulated in properties that can be well-preserved after rectification (e.g., pulse position) such that information can be decoded from the energy harvester output.
			\end{itemize}

			The most popular architectures in the literature are \gls{ts} and \gls{ps} due to their practicality and tractability.
			The \gls{r-e} region of the former can be inferred from that of the latter, since the \gls{wit}-only and \gls{wpt}-only vertices in \gls{ts} correspond to $\rho=1$ and $\rho=0$ in \gls{ps}, respectively.
			Integrated receiver eliminates the need of \gls{rf} chains and advanced architectures, but experiences information degradation and works better for low-throughput applications.
		\end{subsubsection}
	\end{subsection}
\end{section}
